Data preprocessing: raw data to processed data

### 2023-03-23 preprocessing/ecaw_raw_processed_preprocessing.Rmd
updated data preprocessing files so the codebooks are done and the full dataset is saved for supplementary materials d

@@

These responses will be included in an exploratory analysis that will be published in supplementary materials D.

At the end of the exclusion we had `r nrow(raw)` responses remaining for the analysis.

There were `r filter(raw, has_missing) %>% nrow()` respondents who had at least one missing value in the main questions of interests.

@@

For creating the codebook we will use the codebook created for the source data.

```{r message=FALSE}
codebook <-
  read_csv(here("data/source/ecaw_221102_source_codebook.csv")) %>% 
  select(-original_var_name) %>% 
  rename(var_name = new_var_name) %>% 
  filter(var_name %in% colnames(raw))

# Save the codebook
readr::write_csv(codebook, here("data/raw/ecaw_raw_codebook.csv"))
```

>>>>

However, these responses will be included in an exploratory analysis that will be published in supplementary materials D. So we save them separately before exclusion.

```{r}
processed_all <- 
  raw %>%
  mutate(duration_in_mins = duration_in_seconds / 60) %>%
  select(
    -start_date,
    -end_date,
    -status,
    -progress,
    -finished,
    -duration_in_seconds,
    -recorded_date,
    -distribution_channel,
    -user_language
  )

readr::write_csv(processed_all, here("data/processed/ecaw_processed_all_data.csv"))
```

The full dataset that we are going to use to calculate the results in Supplement D includes `r nrow(processed_all)` responses.

We create a simple codebook for this dataset.

```{r}
processed_all_codebook <-
  read_csv(here("data/source/ecaw_221102_source_codebook.csv")) %>% 
  select(-original_var_name) %>% 
  rename(var_name = new_var_name) %>% 
  filter(var_name %in% colnames(processed_all)) %>% 
  # Adding new column descriptions
  mutate(
    has_missing = "True if respondent has any missing responses.",
    duration_in_mins = "Time spent from opening the survey to closing it in minutes."
  )

readr::write_csv(processed_all_codebook, here("data/processed/ecaw_processed_all_codebook.csv"))
```

Excluding the respondents who did not finish the questionnaire.

@@

At the end of the exclusion we had `r nrow(raw)` responses remaining for the analysis. There were `r filter(raw, has_missing) %>% nrow()` respondents who had at least one missing value in the main questions of interests.

@@

For creating the codebook for the processed data we will use the codebook created for the source data.

```{r message=FALSE}
codebook <-
  read_csv(here("data/source/ecaw_221102_source_codebook.csv")) %>%
  select(-original_var_name) %>%
  rename(var_name = new_var_name) %>%
  filter(var_name %in% colnames(raw)) %>%
  # Adding new column descriptions
  mutate(
    has_missing = "True if respondent has any missing responses.",
    duration_in_mins = "Time spent from opening the survey to closing it in minutes."
  )

# Save the codebook
readr::write_csv(codebook, here("data/processed/ecaw_processed_codebook.csv"))
```
